### 2020-06-03 5_evaluation.tex
Fiddle with figure placement.
Some new text and tweaks for space.

For GPU experiments we use the Piz Daint supercomputer~\cite{PizDaint}, a Cray XC50 with
one Intel Xeon E5-2690 v3 (12 physical cores) and one NVIDIA Tesla
P100 per node. We use GCC 6.2.0, Cray MPICH 7.7.2, and
CUDA 9.1.85.

@@

Figure~\ref{fig:flops}, which is the full version of
Figure~\ref{fig:flops-mpi}, shows the FLOP/s achieved with a compute-bound
kernel with varying problem sizes (simulated by running the kernel for varying numbers of iterations). Each data point in the graph is the mean of 5 runs, with Task Bench configured to execute 1000 time steps of the stencil pattern. In the best case, we measure peak FLOP/s of
$1.26 \times 10^{12}$, which compares favorably with the officially
reported number of $1.2 \times 10^{12}$ \cite{Cori}. For the purposes
of measuring efficiency, we use our empirically determined number as
the baseline for 100\% efficiency.

Most systems achieve or nearly achieve peak FLOP/s. Some
systems reserve a number of cores (usually 1 or 2) for internal
use; these systems take a minor hit in peak FLOP/s compared
to systems that share all cores between the application and runtime. Some of the
higher-overhead systems struggle to achieve peak FLOP/s, though in most cases
the curves suggest that performance would continue to improve if we
were to run larger problem sizes. Unfortunately, the excessive
computational cost of running such tests makes this prohibitively
expensive. For example, the Spark job in
this case ran for over 6 hours.

@@

Not all cores are required to saturate memory bandwidth, reducing the
impact of reserving cores for internal use. Most systems hit 100\% of
peak, unlike the compute-bound case.

@@

To answer this question, we use METG %% to determine the
%% smallest task granularity that can be executed at a given level of
%% efficiency
as a proxy for overhead. Figure~\ref{fig:metg-compute}
shows how METG(50\%) varies with node count for a variety of
dependence patterns supported by Task Bench. METG(50\%) is calculated
separately at each node count, to distinguish runtime system behavior from
changes in communication latencies and topology when using
progressively larger portions of the machine.

@@

We observe that the baseline overheads of different
systems vary by over 5 orders of magnitude. It is worth
remembering when considering this metric that this is a \emph{minimum}
effective task granularity. Applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical task granularities will
generally be determined by the application domain being
considered. Most notably, for large-scale data analytics workloads, the higher METG values observed for Spark and
TensorFlow are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.

The least complicated pattern (stencil) is most favorable
to MPI, as it provides no
opportunity for task parallelism. The
dominating factor in this case is the overhead of executing a task, which is
minimal for MPI as the Task Bench implementation simply executes tasks in alternation with
communication phases. The asynchronous
mechanisms of other systems are pure overhead in this scenario.
The gap between MPI and other systems shrinks as complexity grows, and even reverses as task parallelism is
added in the form of multiple task graphs.

Spark and Swift/T
are omitted from comparisons with more complicated dependencies, as the overheads of these systems require
excessive problem sizes (beyond what can be completed in 6
hours) to reach 50\% efficiency.

>>>>

For GPU experiments we use Piz Daint~\cite{PizDaint}, a Cray XC50 with
a Intel Xeon E5-2690 v3 (12 physical cores) and one NVIDIA Tesla
P100 per node. We use GCC 6.2.0, Cray MPICH 7.7.2, and
CUDA 9.1.85.

@@

Figure~\ref{fig:flops}, which is the full version of
Figure~\ref{fig:flops-mpi}, shows the FLOP/s achieved with a compute-bound
kernel with varying problem sizes (simulated by running the kernel for varying numbers of iterations). Each data point in the graph is a mean of 5 runs, with Task Bench configured to execute 1000 time steps of the stencil pattern. In the best case, we measure peak FLOP/s of
$1.26 \times 10^{12}$, which compares favorably with the officially
reported number of $1.2 \times 10^{12}$ \cite{Cori}. We use our empirically determined number as
the baseline for 100\% efficiency below.

Most systems achieve or nearly achieve peak FLOP/s. Some
systems reserve a number of cores (usually 1 or 2) for internal
use (see below); these systems take a minor hit in peak FLOP/s compared
to systems that share all cores between application and runtime. Some
higher-overhead systems struggle to achieve peak FLOP/s, though in most cases
the curves suggest that performance would continue to improve if we
were to run larger problem sizes. Unfortunately, the excessive
computational cost of running such tests makes this prohibitively
expensive. For example, the Spark job in
this case ran for over 6 hours.

@@

Not all cores are required to saturate memory bandwidth. {\color{blue}
  This reduces the impact of reserving cores for system use
  (e.g. task-based systems that perform dependence analysis).} Nearly
all systems hit 100\% of peak, unlike the compute-bound case.

@@

To answer this question, we use METG %% to determine the
%% smallest task granularity that can be executed at a given level of
%% efficiency
as a proxy for overhead. Figure~\ref{fig:metg-compute}
shows how METG(50\%) varies with node count for a subset of
dependence patterns supported by Task Bench. METG(50\%) is calculated
separately at each node count, to distinguish runtime system behavior from
changes in communication latency and topology when using
progressively larger portions of the machine.

@@

We observe that overheads vary by over 5 orders of
magnitude. {\color{blue} The most efficient systems are explicitly parallel
and provide very lightweight mechanisms for parallelism. Task-based systems for HPC tend to be next most efficient, and
provide additional features such as automatic dependency discovery and
data movement. Slower systems tend to be designed primarily for
large-scale data analysis or workflows.} It is worth
remembering that these are \emph{minimum}
effective task granularities. Applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical task granularities will
generally be determined by the application domain being
considered. Most notably, for large-scale data analytics workloads, the higher METG values observed for Spark and
TensorFlow are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.

The least complicated pattern (stencil) is most favorable
to MPI, as it provides no
opportunity for task parallelism. The
dominating factor in this case is the overhead of executing a task, which is
minimal for MPI as the code simply executes tasks in alternation with
communication. The asynchrony
of other systems is pure overhead in this scenario.
MPI's advantage shrinks as complexity grows, and even reverses as task parallelism is
added in the form of multiple task graphs.

We omit Spark and Swift/T
with more complicated dependencies, as their higher overheads require
excessive problem sizes (beyond what completes in 6
hours) to reach 50\% efficiency.
